Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-05-16 paper/ms.tex
update ms

Figure~\ref{fig:agescalecompone} shows the result of a literature comparison against
ages reported by \citet{Berger_2020a_catalog}, \citet{2021AJ....161..189L}, 
 \citet{2023ApJ...952..131M}, and
\citet{2024AJ....167..159L}.
We followed any guidance available from these respective studies for removing ages
that were flagged as unreliable.
Rather than compare the ages of the stars directly against each other, we then decided
to compare them against a common benchmark: open clusters.

Cluster memberships are a delicate subject.
Figure~\ref{fig:agescalecompone} is in fact showing putative ages for a set of putative cluster members.
For NGC6811 and NGC6819, we adopted all reported members from \citet{2018A&A...618A..93C,CantatGaudin_2020} and \citet{Kounkel_2020}. 
For Melange-3 we used the members from \citet{2022AJ....164...88B} and required ``offset'' tangential velocities below 2\kms.
For Cep-Her we used stars from Table~2 of \citet{Bouma_2022b}, requiring ``weights'' exceeding 0.1.
These cluster lists almost certainly include non-members, in fractions that we do not aim to quantify.
Even with these contaminants, we can compare the relative age distributions derived by
the different studies.

There are two main metrics for success in this test:
the first is the extent to which the reported ages agree with the cluster age (accuracy).
The second concerns how precise the reported ages are, and whether that precision agrees with the observed
distribution of ages around unity.

@@

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{merged_lit_ages_vs_cluster_ages.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Literature age scale comparison.}
    Each point denotes the reported age of a star observed by Kepler,
    normalized by the age of a stellar ensemble in which the star
    is a putative member.
    Rows show the available stellar ensembles, and
    columns show the various age-measurement techniques described in Appendix~\ref{app:litagecomparison}.
    Stars are sorted according to their median reported ages.
    Note that the horizontal axis is logarithmic; the first dotted line
    to the right of unity corresponds to a reported age ten times older
    than the cluster age.
	}
	\label{fig:agescalecompone}
\end{figure*}

>>>>

Figure~\ref{fig:agescalecompone} shows the result of a literature
comparison against ages reported by \citet{Berger_2020a_catalog},
\citet{2021AJ....161..189L}, \citet{2023ApJ...952..131M}, and
\citet{2024AJ....167..159L}.
We followed any guidance available from these respective studies for
removing ages that were flagged as unreliable.
Rather than comparing the ages of the stars directly against each other,
we compared them against a common benchmark: open clusters.

Cluster memberships are a delicate subject.
Figure~\ref{fig:agescalecompone} is showing putative ages for
a set of putative cluster members.  For NGC6811 and NGC6819, we
adopted candidate members from
\citet{2018A&A...618A..93C,CantatGaudin_2020} and
\citet{Kounkel_2020}. 
For Melange-3 we used the candidate members reported by
\citet{2022AJ....164...88B} and required ``offset'' tangential
velocities below 2\kms.  For Cep-Her we
used candidate members from Table~2 of \citet{Bouma_2022b}, requiring
``weights'' exceeding 0.1.
These lists almost certainly include non-members, in fractions that we
do not aim to quantify.  Even with these contaminants, we can compare
the relative age distributions derived by the different studies.

There are two main metrics for success in this test: the first is
whether the reported ages agree with the cluster age (accuracy).  The
second is whether the reported age precisions agree with their
dispersion around the cluster age.

@@

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.98\textwidth]{merged_lit_ages_vs_cluster_ages.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Literature age scale comparison.}
    Each point denotes the reported age of a star observed by Kepler,
    normalized by the age of a stellar ensemble in which the star
    is a candidate member.
    Rows show the available stellar ensembles, and columns show the
    various age-measurement techniques described in
    Appendix~\ref{app:litagecomparison}.
    Stars are sorted according to their median reported ages, and
    clusters are sorted by descending richness.
    Note that the horizontal axis is logarithmic; the first dotted line
    to the right of unity corresponds to a reported age ten times older
    than the cluster age.
	}
	\label{fig:agescalecompone}
\end{figure*}
